### 2021-03-17 paper.Rmd
fix paths

\begin{figure*}[!ht]
   \centering
         \includegraphics[width=0.45\textwidth]{figures/ggobi_book/brush_query.pdf}
         \includegraphics[width=0.45\textwidth]{figures/ggobi_book/brush_response.pdf}
\caption{When a user brushes data on the left panel, points that fall inside the region are highlighted in orange. The view on the right responds by higlighting the corresponding points.}
\label{fig:brushing}
\end{figure*}

>>>>

\begin{figure*}[!ht]
   \centering
         \includegraphics[width=0.45\textwidth]{figures/ggobi_book/brush-query.pdf}
         \includegraphics[width=0.45\textwidth]{figures/ggobi_book/brush-response.pdf}
\caption{When a user brushes data on the left panel, points that fall inside the region are highlighted in orange. The view on the right responds by higlighting the corresponding points.}
\label{fig:brushing}
\end{figure*}
